LOINC2HPO_EPIC AND SCC

### 2022-04-28 code/r/01_A_MSDW_HPO_Phenotype_Analysis.Rmd
observed normalized by tested

  p <- df %>% filter(termid %in% terms_of_interest) %>% 
    filter(lab_year <= 2019 & lab_year > 2000) %>%
    ggplot(aes(x = lab_year, y = eval(parse(text=y_str)), group = termid, color = termid)) + 
    geom_point() +
    geom_line() +
    scale_color_discrete(breaks = hpo_terms_selected$termid, labels = str_c(hpo_terms_selected$termid, hpo_terms_selected$label, sep = " ")) +
    xlab('Year') +
    ylab(y_label) +
    theme_bw() +
    theme(panel.grid = element_blank(),
        axis.title = element_text(size = 8), axis.text = element_text(size = 8), 
        legend.text = element_text(size = 8), legend.title = element_text(size = 10))

>>>>

  p <- df %>% filter(termid %in% terms_of_interest) %>% 
    filter(lab_year <= 2019 & lab_year > 2000) %>%
    ggplot(aes(x = lab_year, y = eval(parse(text=y_str)), group = termid, color = termid)) + 
    geom_point() +
    geom_line() +
    scale_color_discrete(breaks = hpo_terms_selected$termid, labels = str_c(hpo_terms_selected$termid, hpo_terms_selected$label, sep = " ")) +
    xlab('Year') +
    ylab(y_label) +
    theme_az()
